Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''

### 2014-11-20 egpaper_supp.tex
Supplementary material pdf

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{algorithm2e}
\usepackage{rotating}
\usepackage[space]{grffile}
\usepackage[font=small,skip=0pt]{caption}
%\DeclareMathOperator{\Tr}{Tr}
% Include other packages here, before hyperref.

@@

\section{3D Object Dataset}
\label{sect:3dobject}
We run our ensemble of NZ-WHO templates as a detector on 3D Object
dataset\cite{savarese07} without tuning and present detection average precision, average
viewpoint precision, viewpoint confusion matrix and mean precision in pose
estimation. See Fig.~\ref{fig:3dobject_ap}

Most of the error in viewpoint estimation come from frontal and back views

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{supp/car_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (a) Car\\
  \includegraphics[width=0.99\linewidth]{supp/bicycle_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (b) Bicycle\\
  \caption{Detection and pose estimation on 3D Object dataset car category (top) and bicycle category (bottom).
  Average Precision (red) and Average Viewpoint Precision (green) (left)
  Viewpoint confusion table and MPPE (right), Viewpoint index 1 is front, index 2 is
  front-right, \dots index 8 is front-left. }
  \label{fig:3dobject_ap}
\end{figure}

We put successful car detection results on Fig.~\ref{fig:3dobject_car_good} and
failure cases on Fig.~\ref{fig:3dobject_car_bad}. And for bicycle, successful
bicycle detection results are on Fig.~\ref{fig:3dobject_bicycle_good} and
failure cases on Fig.~\ref{fig:3dobject_bicycle_bad}.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car32.png} &
  \includegraphics[width=0.40\linewidth]{supp/car26.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car10.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
  \includegraphics[width=0.40\linewidth]{supp/car8.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car20.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car31.png} \\
%   \includegraphics[width=0.40\linewidth]{supp/car33.png} & 
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset car
category. In each column, original image (left) and detection result overlaid on
top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_car_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset car
classes. In each column, original image (left) and detection result overlaid on
top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
  \includegraphics[width=0.40\linewidth]{supp/car30.png} \\ 
  \includegraphics[width=0.40\linewidth]{supp/car18.png} &
  \includegraphics[width=0.40\linewidth]{supp/car25.png} \\
  \hline
  \end{tabular}
\caption{Failed pose estimation results on 3D Object dataset car and bike
classes. In each column, original image (left) and detection result overlaid on
top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
\hline 
  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle20.png} \\
\hline
\end{tabular}
\caption{Failed pose estimation results on 3D Object dataset car and bike
classes. In each column, original image (left) and detection result overlaid on
top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bicycle_bad}
\end{figure*}

@@

We run our ensemble of NZ-WHO templates as a detector on car
and bicycle classes in PASCAL3D+ dataset  \cite{Xiang14} and present detection average precision,
average viewpoint precision, viewpoint confusion matrix and mean precision in
pose estimation. See Fig.~\ref{fig:3dobject_ap}

For each of the proposal bounding box, we assumed that there is only one object and the object 
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
  \includegraphics[width=0.24\linewidth]{supp/occlusion1b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car1a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car1b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car3a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car3b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car5a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car5b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car6a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car6b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car7a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car7b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car10a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car10b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car16a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car16b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car17a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car17b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car19a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car19b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car21a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car21b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car22a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car22b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car18a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car18c.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18d.png} \\
  \hline
  \end{tabular}
\caption{Successful detection result on PASCAL3D+ dataset car class, First tow columns are the original images and second column detection result overlaid on top. }
  \label{fig:pascal3d_car_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12b.png}  \\
  \hline
  \end{tabular}
\caption{Successful detection result on PASCAL3D+ dataset car class, First tow columns are the original images and second column detection result overlaid on top. }
  \label{fig:pascal3d_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2b.png} & 
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car8b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car9a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car9b.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car12b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car14b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car15a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car15.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car20a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car20b.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23b.png} \\
  \hline
  \end{tabular}
\caption{Detection failure results on PASCAL3D+ dataset car class}% with a bounding box and corresponding confidence score (right).}
  \label{fig:pascal3d_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14b.png} & 
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15a.png}  &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17b.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19b.png}  \\   \hline
  \end{tabular}
\caption{Detection Result on PASCAL3D+ dataset car class}% with a bounding box and corresponding confidence score (right).}
  \label{fig:pascal3d_bicycle_bad}
\end{figure*}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{algorithm2e}
\usepackage{rotating}

\usepackage[space]{grffile}
\usepackage[font=small,skip=0pt]{caption}
%\DeclareMathOperator{\Tr}{Tr}
% Include other packages here, before hyperref.

@@

\section{3D Object Dataset}
\label{sect:3dobject}

It this section, we provide qualitative examples and plots for the experiment
``2D-3D Matching as an Object Detector''. To recapitulate, we run our ensemble
of NZ-WHO templates as an ensemble of exemplar templates on 3D Object
dataset\cite{savarese07} without fine-tuning stage. The detection average
precision, average viewpoint precision, viewpoint confusion matrix and mean
precision in pose estimation results are on Fig.~\ref{fig:3dobject_ap}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{supp/car_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (a) Car\\
  \includegraphics[width=0.99\linewidth]{supp/bicycle_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (b) Bicycle\\
  \caption{Detection and pose estimation on 3D Object dataset car category (top) and bicycle category (bottom).
  Average Precision (red) and Average Viewpoint Precision (green) are overlaid on the left plot and
  viewpoint confusion table and MPPE are on the right plot. The viewpoint index 1 is front, index 2 is
  front-right, \dots index 8 is front-left.}
  \label{fig:3dobject_ap}
\end{figure}

For qualitative results, we put successful car viewpoint prediction results on
Fig.~\ref{fig:3dobject_car_good} and
failure cases on Fig.~\ref{fig:3dobject_car_bad}. And for bicycle, successful
results are on Fig.~\ref{fig:3dobject_bicycle_good} and
failure cases on Fig.~\ref{fig:3dobject_bicycle_bad}. We followed detection
and viewpoint estimation criteria of \cite{Xiang12} where detection is correct
iff intersection over union of more than 0.5 and viewpoint estimation is
correct iff detection is correct \emph{and} azimuth of the viewpoint
prediction falls in to the correct viewpoint bin.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car32.png} &
  \includegraphics[width=0.40\linewidth]{supp/car26.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car10.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
  \includegraphics[width=0.40\linewidth]{supp/car8.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car20.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car31.png} \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset, car
category. In each column, original image is on the left and detection result overlaid on
the right.}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_car_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset, bicycle
category. In each column, original image is on the left and detection result overlaid on
the right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
  \includegraphics[width=0.40\linewidth]{supp/car30.png} \\ 
  \includegraphics[width=0.40\linewidth]{supp/car18.png} &
  \includegraphics[width=0.40\linewidth]{supp/car25.png} \\
  \hline
  \end{tabular}
\caption{Failed detection or pose estimation results on 3D Object dataset, car
category. In each column, original image is on the left and detection result overlaid
on the right.}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
\hline 
  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle20.png} \\
\hline
\end{tabular}
\caption{Failed detection or pose estimation results on 3D Object dataset, bicycle
category. In each column, original image is on the left and detection result overlaid on
the right.}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bicycle_bad}
\end{figure*}

@@

It this section, we provide qualitative examples and plots for the experiment
``Enriching Existing Detection''. To recapitulate, we used object detection
bounding boxes from state-of-the-art detectors \cite{Girshick14, Pepik12} and
enrich bounding boxes with 2D-3D registration and continuous viewpoint
estimation. We present detection average precision, average viewpoint
precision, viewpoint confusion matrix and mean precision in pose estimation
results on Fig.~\ref{fig:pascal_ap}.

We followed the evaluation criteria of \cite{Xiang14} for detection and
viewpoint estimation.

In this experiment, we used R-CNN\cite{Girshick14} for detection bounding box
proposals and our system produces accurate 2D-3D matching on the proposal
regions. We used $15\%$ context (extend the proposal region by $15\%$ on the
top, right, left and bottom). We run our pipeline on PASCAL3D+
dataset\cite{Xiang14} with fine-tuning stage.

If our method fails to estimate viewpoint (confidence score is below 45), it
estimates 0 azimuth, 0 elevation, 0 yaw. Note that for all categories and
different number of viewpoints, our method has difficulty discerning frontal
view and back view.

\begin{figure*}[h]
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn8_crop.png}\\
    (a) Car, 4 views&
    (b) Car, 8 views\\
  \includegraphics[width=0.45\linewidth]{car_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn24_crop.png}\\
    (c) Car, 16 views&
    (d) Car, 24 views\\
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn8_crop.png}\\
    (e) Bicycle, 4 views&
    (j) Bicycle, 8 views\\  
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn24_crop.png}\\
    (g) Bicycle, 16 views&
    (h) Bicycle, 24 views\\
  \end{tabular}
  \caption{Detection and pose estimation on PASCAL3D+ dataset. On the left, we
  present average precision curve (red) average viewpoint precision curve
  (green). On the right, we present confusion matrix and mean precision in pose
  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
  $n-1$ is front-left for number of viewpoints $n$.}
  \label{fig:pascal_ap}
\end{figure*}

We put qualitative results on Fig.~\ref{fig:pascal3d_car_good} to
Fig.~\ref{fig:pascal3d_bicycle_bad}.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
  \includegraphics[width=0.24\linewidth]{supp/occlusion1b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car1a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car1b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car3a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car3b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car5a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car5b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car6a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car6b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car7a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car7b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car10a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car10b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car16a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car16b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car17a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car17b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car19a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car19b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car21a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car21b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car22a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car22b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car18a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car18c.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18d.png} \\
  \hline
  \end{tabular}
  \caption{Successful detection and pose estimation result on PASCAL3D+ dataset
  car category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_car_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12b.png}  \\
  \hline
  \end{tabular}
\caption{Successful detection and pose estimation result on PASCAL3D+ dataset
  bicycle category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2b.png} & 
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car8b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car9a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car9b.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car12b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car14b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car15a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car15.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car20a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car20b.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23b.png} \\
  \hline
  \end{tabular}
\caption{Failed detection or pose estimation result on PASCAL3D+ dataset
  car category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14b.png} & 
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15a.png}  &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17b.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19b.png}  \\   \hline
  \end{tabular}
\caption{Failed detection or pose estimation result on PASCAL3D+ dataset
  bicycle category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_bicycle_bad}
\end{figure*}

\section{Fine Tuning}

In this section, we give qualitative examples of before and after the
fine-tuning stage on Fig.~\ref{tuning}.

See section ``Pose Fine-Tuning via MCMC'' for more detail.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{ccc}
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_2b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_2c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
  \end{tabular}
\caption{From left to right, original images, initial pose estimations and
fine-tuned result. The numbers, from the left, indicate detection confidence
and intersection over union respectively.} 
  \label{fig:tuning}
\end{figure*}
